<<<<<<< HEAD
---
title: "Super Awesome Project Template"
output: word_document
date: "2023-03-31"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section One Julia

```{r student1}
library(rvest)
country_url <- "https://en.wikipedia.org/wiki/List_of_Billboard_number-one_country_songs_of_2023"
html <- read_html(country_url)
cast <- html_nodes(html, "td:nth-child(3) .fn a , th+ td > a")

html_text(cast, trim = TRUE)

```


## Section Four Sophie 

```{r student4}
urlfunction <- function(year) {
country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Billboard_number-one_country_songs_of_",  year)
html <- read_html(country_url)
cast <- html_nodes(html, "td:nth-child(3) .fn a , th+ td > a")

html_text(cast, trim = TRUE) 


}

for (i in 1958:2023) {
  urlfunction(i)
}

``` 

## Section Two Tessa

```{r student2}

```

## Section Three Eva

```{r student3}
library(rvest)
# 1958, 2012-2023
url1_years <- c(1958, 2012:2023)
url1 <- "https://en.wikipedia.org/wiki/List_of_Billboard_number-one_country_songs_of_"

urlfunction1 <- function(year) {
country_url <- paste0(url1, year)
html <- read_html(country_url)
cast <- html_nodes(html, "td:nth-child(3) .fn a , th+ td > a")

html_text(cast, trim = TRUE) 
}
for (i in url1_years) {
  urlfunction1(i)
}

# 1959-1961
url2_years <- c(1959:1961)
url2 <- "https://en.wikipedia.org/wiki/List_of_Hot_C%26W_Sides_number_ones_of_"

urlfunction2 <- function(year) {
country_url <- paste0(url2, year)
html <- read_html(country_url)
cast <- html_nodes(html, ".jquery-tablesorter span a , .jquery-tablesorter th a")

html_text(cast, trim = TRUE) 
}
for (i in url2_years) {
  urlfunction2(i)
}

# 1962-1989
url3_years <- c(1962:1989)
url3 <- "https://en.wikipedia.org/wiki/List_of_Hot_Country_Singles_number_ones_of_"

urlfunction3 <- function(year) {
country_url <- paste0(url3, year)
html <- read_html(country_url)
cast <- html_nodes(html, ".fn a , td > a")

html_text(cast, trim = TRUE) 
}
for (i in url3_years) {
  urlfunction3(i)
}

# 1990-2004
url4_years <- c(1990:2004)
url4 <- "https://en.wikipedia.org/wiki/List_of_Hot_Country_Singles_%26_Tracks_number_ones_of_"

urlfunction4 <- function(year) {
country_url <- paste0(url4, year)
html <- read_html(country_url)
cast <- html_nodes(html, ".jquery-tablesorter th+ td a , .jquery-tablesorter th a")

html_text(cast, trim = TRUE) 
}
for (i in url4_years) {
  urlfunction4(i)
}

# 2005-2011
url5_years <- c(2005:2011)
url5 <- "https://en.wikipedia.org/wiki/List_of_Hot_Country_Songs_number_ones_of_"

urlfunction5 <- function(year) {
  country_url <- paste0(url5, year)
html <- read_html(country_url)
cast <- html_nodes(html, ".jquery-tablesorter th+ td a , .jquery-tablesorter th a")

html_text(cast, trim = TRUE) 
}
for (i in url5_years) {
  urlfunction5(i)
}


```

```{r}
urlfunction1(2012)
```


## Section Four Sophie 

```{r student4}
urlfunction <- function(year) {
country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Billboard_number-one_country_songs_of_",  year)
html <- read_html(country_url)
cast <- html_nodes(html, "td:nth-child(3) .fn a , th+ td > a")

html_text(cast, trim = TRUE) 


}

for (i in 1958:2023) {
  urlfunction(i)
}

```
