---
title: "Final Project - Song Repetitiveness"
author: "Eva, Julia, Sophie, and Tessa"
date: "2024-05-07"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(stringr)
library(tidytext)
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)
```


### For this project, our goal was to gather song data, and then analyze the song lyrics for repetitiveness in various ways. <br>
•	To start, we scraped Billboard Top 100 song data off of Wikipedia and created a data frame with some basic information about each song. <br>
•	We then used the data frame of songs to write a function to gather corresponding lyrics from the lyric hosting website www.songlyrics.com. <br>
•	Once we had our cleaned-up data frame of song information, we were then able to create functions to measure receptiveness and show them through multiple graphical visuals. <br>


### Justifications of choices: <br>
•	We picked Wikipedia for our top songs data frame without lyrics because we could gather songs easily and compare them across years <br>
•	We used as many years as Wikipedia had available for Country which was from 1958 to 2023 and for Hip Hop which was from 1986 to 2023 <br>
•	During the lyric scraping process, our goal was to maximize the number of songs we could access lyrics for. <br>
•	The suggested lyric hosting website www.songlyrics.com had the simplest URL to create a function to scrape the lyrics. <br>
•	We manipulated the song titles and artists to match the URL format. <br>
• Some lyrics could not be scraped because they were not up to date or the website did not contain the song's lyrics. <br>
•	Because the website was not up to date we were unable to collect Country song's lyrics for 2019-2023 and we decided this was acceptable because we had so many songs from other years. <br>
•	After creating the data frames we chose to visualize song repetition by analyzing unique words and title repetitions over time. In both measures of repetitiveness, we looked at averages per year. Through averages, we were able to see stronger trends and repetition patterns. <br>
• We chose unique word ratio because we wanted to find the repetitiveness of singular words within the lyrics, and we wanted to see how many words stood out. <br>
• For titles we chose to look at how often the titles repeated and if we could see a trend or if it has always been consistent. <br>
• We compared this between genres and if it is a common thing artists do in general <br>
• In the title repetition measurement, we incorporated linear models and r-squared statistics to further investigate patterns. <br>

```{r, echo=FALSE}
## Country Data
## input: a year
##output and purpose: creating a data frame of the top country songs from that year from wikipedia urls
urlfunction <- function(year) {
  if (year == 1958 || (year >= 2012 && year <= 2023)) {
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Billboard_number-one_country_songs_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, "td:nth-child(3) .fn a , th+ td > a")
  }else if (year >= 1959 && year <= 1961){
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_C%26W_Sides_number_ones_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, ".jquery-tablesorter span a , .jquery-tablesorter th a")
  }else if (year >= 1962 && year <= 1989) {
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_Country_Singles_number_ones_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, ".fn a , td > a")
  }else if (year >= 1990 && year <= 2004) {
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_Country_Singles_%26_Tracks_number_ones_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, ".jquery-tablesorter th+ td a , .jquery-tablesorter th a")
  }else { 
    country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_Country_Songs_number_ones_of_",  year)
    html <- read_html(country_url)
    cast <- html_nodes(html, ".jquery-tablesorter th+ td a , .jquery-tablesorter th a")
  }  

  html_text(cast, trim = TRUE) 
  tables <- html_table(html, fill = TRUE, header = TRUE)
  desired_table <- tables[[1]]
  desired_table <- desired_table[, c(2, 3)]
    #include only the second and third columns which are title and artist
  if ("Title" %in% desired_table[1, ]) {
    desired_table <- desired_table[-1, ]
    #get rid of top row if they have an extra header row
          }
  colnames(desired_table) <- c("Title", "Artist")
    #name columns
  desired_table$Year <- year
     #add column for year
  desired_table$Genre <- "Country" 
     #add column for genre
  desired_table <- unique(desired_table)
    #get rid of repeat rows
  return(desired_table)
      
}
```


```{r, echo=FALSE, warning= FALSE}
## Hip Hop Data
#input: a year
#output and purpose: create a table of the top rap songs from that year from wikipedia urls
urlfunctionHipHop <- function(year) {
  if (year >= 2007 && year <= 2023) {
      HipHop_url <- paste0("https://en.wikipedia.org/wiki/List_of_number-one_R%26B/hip-hop_songs_of_", year, "_(U.S.)")
      #specific url for years 2007-2023
      html <- read_html(HipHop_url)
      cast <- html_nodes(html, "th , .plainrowheaders td")
      html_text(cast, trim = TRUE) 
      tables <- html_table(html, fill = TRUE, header = TRUE)
      
      if (year == 2012 || year == 2019) {
        #the table containing the artist and song title from the website differed for the year 2012 and 2019
        desired_table <- tables[[1]]
      }else{
        desired_table <- tables[[2]]
      }
      desired_table <- desired_table[, -1]
        #taking out an unnecessary first column
  }else {
      #specific url for every year before 2007
      HipHop_url <- paste0("https://en.wikipedia.org/wiki/", year, "_in_hip_hop_music")
      html <- read_html(HipHop_url)
      cast <- html_nodes(html, ".headerSort , .jquery-tablesorter td, .headerSort") 
      html_text(cast, trim = TRUE) 
      tables <- html_table(html, fill = TRUE, header = TRUE)
      #accessing the desired table
      if (year == 2000 || year >= 2002) {
        #the table containing the artist and song title from the website differed for years 2000 and from 2002-2006
        desired_table <- tables[[5]]
      }else{
        desired_table <- tables[[6]]
      }
  }
  colnames(desired_table) <- c("Title", "Artist")
    #name columns
  desired_table$Year <- year
     #add columns for year
  desired_table$Genre <- "Hip Hop" 
     #add column for genre
  desired_table <- unique(desired_table)
     #take out repeated rows
  return(desired_table)
}


```


```{r, echo=FALSE}
## function to clean up data frames without lyrics into a nice format
clean_data <- function(dataset) {
    #input: a data set
    #output and purpose: clean up the data set for creating urls in the 
    dataset$Title<-gsub("/.*", "", dataset$Title)
      #remove everything after / in the title
    dataset$Title<-gsub('"', '', dataset$Title)  
      #remove double quotation marks
    dataset$Artist <- gsub("featuring", "feat", dataset$Artist)
      #replace the word featuring with feat for lyrics url
    dataset <- lapply(dataset, function(x) gsub(" ", "-", x))
      #replace spaces with hyphens
    dataset <- as.data.frame(dataset)
      #turn dataset into a data frame
    dataset$Title <- sub("-$", "", dataset$Title)
      #remove hyphens at the end of the title column
    dataset$Title <- gsub("[,.?%()]", "", dataset$Title)
      #remove special characters from title column
    dataset$Artist <- gsub("[.']", "", dataset$Artist)
      #remove periods and apostrophes 
    dataset$Artist <- sub("-and", "", dataset$Artist)
      #remove all ands from end of artist names
    dataset <- dataset[!duplicated(dataset$Title), ]
      #delete songs that showed up as top songs in more then one year
    return(dataset)
}

```


```{r, echo=FALSE}
## Function to add the lyrics to data frame
# Purpose: This function scrapes lyrics from songlyrics.com for the billboard top 100 country songs 
# Input: Our songs data frame
# Output: A new column in the songs data frame with lyrics for every song
scrape_lyrics <- function(df) {
  lyrics <- character(nrow(df))  
  for (i in 1:nrow(df)) {
    url <- paste0("https://www.songlyrics.com/", df$Artist[i], "/", df$Title[i], "-lyrics/")
    # Tests for errors when getting URLs and makes sure code keeps running after an error occurs
    tryCatch({
      html <- read_html(url)
      raw_lyrics <- html_nodes(html, "#songLyricsDiv") %>% html_text() %>% as.character()
      lyrics[i] <- paste(raw_lyrics, collapse = " ")
    }, error = function(e) {
    })
  }
  df$lyrics <- lyrics  
  return(df)
}
```



```{r, echo=FALSE}
## function to clean lyrics to make into a neat format
#input: data set with song title and artist
#output and purpose: make the data set neater and easily usable for repetition testing
clean_dataLyrics <- function(dataset) {
    dataset <- na.omit(dataset)
    dataset$lyrics <- gsub("\n", " ", dataset$lyrics)
    dataset$lyrics <- gsub("[,.()]", "", dataset$lyrics)
    dataset$lyrics <- tolower(dataset$lyrics)
    dataset <- subset(dataset, !(is.na(lyrics) | lyrics == ""))
    # Replace spaces with hyphens in all columns for URL purposes
    dataset$Artist <- sub("-and", "", dataset$Artist)
    dataset <- subset(dataset, !grepl("we do not have the lyrics for", lyrics))
    # Return the cleaned dataset 
    dataset <- lapply(dataset, function(x) gsub("-", " ", x))
    # Remove rows with missing lyrics
    dataset <- as.data.frame(dataset)
    dataset$Title <- gsub("†", "", dataset$Title)
    dataset$Title <- gsub(' " ', "", dataset$Title)
    return(dataset)
}
```



```{r, eval=FALSE, echo=FALSE}
## Creating data frames with lyrics for hip hop and country
TopCountrySongs <- rbindlist(lapply(1958:2023, urlfunction), fill = TRUE)
   #Creating a dataframe including genre, year, title, artist for 1958 to 2023
TopHipHopSongs <- rbindlist(lapply(1986:2023, urlfunctionHipHop), fill = TRUE)
  TopHipHopSongs <- TopHipHopSongs[,c(1,2,5,6), drop = FALSE]
  #run the function to find tables and put them together from years 1986 to 2023
  #we picked 1986 because this was the first year that there was top hip hop songs in Wikipedia
DFTopCountrySongs <- clean_data(TopCountrySongs)
DFTopHipHopSongs <- clean_data(TopHipHopSongs)

LyricsCountrySongs1 <- scrape_lyrics(DFTopCountrySongs)
LyricsCountrySongs2 <- clean_dataLyrics(LyricsCountrySongs1)
LyricsHipHopSongs1 <- scrape_lyrics(DFTopHipHopSongs)
LyricsHipHopSongs2 <- clean_dataLyrics(LyricsHipHopSongs1)

```


```{r,warning=FALSE,eval=FALSE, echo=FALSE}
#reading into CSVs
#save it as a csv file to working directory

write.csv(LyricsCountrySongs2, "TopCountry.csv", row.names = FALSE)
write.csv(LyricsHipHopSongs2, "TopHipHopSongs.csv", row.names = FALSE)

```

```{r, echo=FALSE}
#call it to test that it works and reads it correctly
TopCountry<-read.csv("TopCountry.csv")
head(TopCountry)

TopHipHopSongsCSV <-read.csv("TopHipHopSongs.csv")
head(TopHipHopSongsCSV)

```


## Measure of Repetitiveness: Unqiue Words Ratio
```{r, warning=FALSE, echo=FALSE}
# UNIQUE RATIO FUNCTION WITH GRAPH
# Purpose: To generate a ratio of unique words to total words within song lyrics for each year included in the data frame and create a ggplot of the resulting data.
# The function inputs: The input of this function is a data frame, which must have columns with "year" and "lyrics". It also take in graph_title which allows you to specifically name your graph.
# The function output: The function return a data frame with columns of year, total words, unique words, and unique ratio. The function will print the graph out showing a trend of unqiue word ratio over time.
generate_unique_ratios_graph <- function(song_df, graph_title) {

generate_unique_ratios <- function(song_df) {
  # make lyrics into single words using tidytext package
  token_lyrics <- song_df %>%
    unnest_tokens(words, lyrics) %>%
    mutate(Year = Year)  # include year data

  # Group by year and calculate unique words ratio
  unique_words_by_year <- token_lyrics %>%
    group_by(Year) %>%  # group lyrics by year
    summarise(total_words = n(), # find total words
              unique_words = n_distinct(words), # find unique words using dplyr (n_distincy)
              ratio = unique_words / total_words) # find ratio of unique words to total words

  return(unique_words_by_year)
}
# low ratio means songs are more repetitive
unique_words_ratios <- generate_unique_ratios(song_df)

# find the overall unique words ratio to add to graph:
overall_unique_words_ratio <-mean(unique_words_ratios$ratio)

# find middle of years so the label is in the middle of the graph
x_midpoint <- median(unique_words_ratios$Year)

# graph unique words ratio over the years
unique_ratio_graph_by_year <-ggplot(unique_words_ratios, aes(x = Year, y = ratio)) +
  geom_line() +
  geom_hline(yintercept = overall_unique_words_ratio, color = "skyblue3") + #add an hline to show when the data is above and below average
  annotate("text", x = x_midpoint, y = overall_unique_words_ratio + 0.01, label = "Average Unique Words Ratio", color = "skyblue3" ) +  # add label to represent what hline means
  labs(title = graph_title,
       x = "Year",
       y = "Unique Words Ratio") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) # center title

return(unique_ratio_graph_by_year)
}

Country_Unique_Ratio_Graph <-generate_unique_ratios_graph(TopCountry, "Unique Words Ratio of Top Country Songs Over Time")
HipHop_Unique_Ratio_Graph <-generate_unique_ratios_graph(TopHipHopSongsCSV, "Unique Words Ratio of Top Hip Hop Songs Over Time")


```
The unique words graph creates a line graph of the average ratio of unique words for each year in the inputted data set. The graph also includes a blue line which represents the overall unique word ratio from all the years. By including this blue line, we can reference when the ratio is above and below average. The unique word ratio represents how much diversity the words have within the lyrics. A low unique word ratio suggests a higher level of repetitiveness within the lyrics.

When looking at the Top Country data we see a high unique word ratio in the earlier years, especially around 1960 it peaks. A high ratio indicates that there are more unique words compared to overall words. Then the graph follows a downward trend and bottoms out around the mid to end 1980s. During this period, we see the most repetitive lyrics, and this could be due to the artists who have top songs. For example, where we see this low unique word ratio there are lots of songs by the band Alabama. Then we continue to see a low ratio in the 1990s and part of this could be because the artist Alan Jackson has multiple top songs within those years. Towards the end of the data, we see the ratio trend back upwards and this could be because Country music has been changing a lot and becoming more pop-like. Another reason could be that there are more artists with top songs throughout the more recent years.

In the Hip Hop graph, we can also see the graph following a similar pattern. We see the unique words ratio start of fairly high, when the genre was new. As the years go on, we see the unique words ratio fall and reach its lowest point in the late 2000s. From then the graph trends back upwards and the lyrics become more unique in recent years. This graph is more difficult to see solid trends and has a lot more variability from year to year. This could be because we have a smaller sample size of Hip Hop songs compared to Country songs. We only have data from 1986 to 2023, compared to the country which is from 1958 to 2019. The variation we see from year to year could be due to how Hip Hop has evolved and that fact that it was a newer genre in the 1980s. Towards the 2000's we collected a lot more data and the songs are becoming a lot less repetitive. This could explained by how Hip Hop music has become a broader genre, and there are a lot more artists entering the genre as well.

## Measure of Repetitiveness: Title Repetition
```{r, warning=FALSE, echo=FALSE}
# TITLE REPETITION FUNCTION WITH GRAPH INCLUDED
# Purpose: To find the number of times a song repeats its title within its own lyrics. Then add the frequency of repeats to the inputted data frame. Lastly it will provide a graph of average title repeats over time with a linear regression model to see if there is a linear relationship.
# The function inputs: The input of this function is a data frame, which must have columns with "Title", "Year", and "lyrics".
# The function output: The function returns the inputted data frame, along with a column called repeats. It will print out a graph showing average title repeats over time with a fitted linear regression model. It will also output some summary statistics of the fitted model.
generate_title_repetition_graph <- function(song_df, graph_title) {
  # Initialize empty column called repeats to hold frquency
  song_df$repeats <- numeric(nrow(song_df))
  
  # for each row in inputted data frame:
  for (i in 1:nrow(song_df)) {
    title <- tolower(song_df$Title[i])  # extract title
    lyrics <- tolower(song_df$lyrics[i]) # extract lyrics
    
    # sum number of times the title is in the lyrics
    title_count <- sum(gregexpr(title, lyrics)[[1]] > 0)
    
    # add repeats count to the existing data frame
    song_df$repeats[i] <- title_count
  }
  
  #create table with average title repeats within each song per year
  ave_title_repeats_by_year <- song_df %>%
    group_by(Year) %>%
    summarize(AveTitleRepeats = mean(repeats))
  
  # plot data by year
  ave_title_repeats <-
    ggplot(ave_title_repeats_by_year, aes(x = Year, y = AveTitleRepeats)) +
    geom_point(size = 1.2) +
    geom_smooth(method = "lm", se = FALSE, color = "skyblue3") +
    labs(title = graph_title,
         x = "Year",
         y = "Mean Title Repeats Per Year") +
    theme_minimal() +
    scale_y_continuous(limits = c(0, NA), breaks = seq(0, max(
      ave_title_repeats_by_year$AveTitleRepeats
    ), by = 5)) + theme(plot.title = element_text(hjust = 0.5))
  
  print(ave_title_repeats)
  
  res2 <- lm(AveTitleRepeats ~ Year, ave_title_repeats_by_year)
  print(paste0("R-squared value for ",graph_title, ": ", summary(res2)$r.squared))
  
}

Country_Title_Repetition <-generate_title_repetition_graph(TopCountry, "Average Title Repeats of Top Country Over Time")
HipHop_Title_Repetition <-generate_title_repetition_graph(TopHipHopSongsCSV, "Average Title Repeats of Top Hip Hop Over Time")

```

The figures above represent the average amount of times each title was repeated within its song lyrics per charting year. For country music we have data that can be visualized from 1958 to 2019. When looking at our plot for country, we can see an upward trend within the points, so we can say that over time song titles are increasingly being repeated in lyrics. We decided to fit a linear model to the data, and after observing the summary statistics we can see that the model fits moderately well with an R squared statistic of 0.2989. Time is explaining about 30% of the variance in title repetition. 

For Hip Hop, we have data that can be visualized from 1987 to 2023. Interestingly enough, we can see a downward trend in the repetition over time. It seems that over time, titles of songs are repeated less on average in lyrics. Unlike country music, a linear model does not fit very well to this model. Time in years can explain about 2.3% of the variance in the data points according to an R-squared statistic of 0.02371 which is very poor. In the figure for Hip Hop, the year 1990 stands out as an outlier because of its high average repetition. In 1990 the top Hip Hop songs included "Ice Ice Baby" by Vanilla Ice, "Have you Seen her","Pray", and "U Can't Touch This" by MC Hammer, and "Just a Friend" by Biz Markie. The lyrics of these songs are extremely repetitive, which explains why this year has a high average. 

Why are song titles being repeated more in Country and less in Hip Hop over time? One inference could be that country artists want to include the title of their songs in their music to enhance the listeners recall and remembrance of the song. Since the 1960s, the way musicians earn profit has changed, and artists may be focusing more on streams instead of selling records and cds. Another could be that over time the genre has shifted into more of a pop culture which is generally more repetitive. For Hip Hop, one inference could be that Hip Hop has grown in popularity over time and because of this, the genre has expanded in many ways. Hip Hop has developed into many sub genres and has become more diverse. 

When comparing the two genres, we do have to keep in mind the fact that our collected country data has a sample size of 1466 that stretches over 61 years, while the Hip Hop genre has a sample size of 394, and only stretches 37 years of observation. Because our data for the country genre holds a larger sample size, we can see more of an accurate representation of trends within the genre. The sample size for Hip Hop is a lot smaller, and so our figures may not fully represent the genre.


## Proportion of Songs Containing Themes Across Genres
```{r, warning=FALSE, echo=FALSE}
alcohol <- c("whiskey", "moonshine", "beer", "wine", "tequila", "vodka", "jack daniels", "budlight", "coorslight", "busch", "alcohol", "rum", "gin", "brandy", "cognac", "schnapps", "absinthe", "champagne", "sake")
intimacy <- c("sexy", "hot", "sex", "attractive", "baby", "babe", "lover", "sweetheart", "passion", "desire", "romance", "affection", "intimacy", "seductive", "lust")
family <- c("mom", "mama", "granny", "marriage", "children", "marry", "wife", "husband", "dogs", "father", "daddy", "grandpa", "grandmother", "aunt", "uncle", "cousin", "siblings", "in-laws", "offspring")
drugs <- c("coke", "cocaine", "tabacco", "weed", "heroin", "methamphetamine", "LSD", "ecstasy", "prescription drugs", "opioids", "hallucinogens", "MDMA", "smoke", "smoking")
guns <- c("gun", "guns", "revolver", "shotgun", "rifle", "pistol", "firearm", "ammunition", "sniper", "handgun", "arsenal", "glock")
music <- c("melody", "rhythm", "harmony", "lyrics", "genre", "beat", "album", "artist", "band", "guitar")
sad <- c("heartbreak", "sorrow", "grief", "despair", "melancholy", "misery", "anguish", "heartache", "depression", "tears")
countylivin <- c("cowboy", "horse", "truck", "pickup", "road", "tea", "tractor", "barn", "ranch", "cattle", "hay", "pasture", "cowboy boots", "western", "yeehaw", "rodeo")
town <- c("small town", "hometown", "back home", "home", "village", "community", "neighborhood", "suburb", "township", "locality", "settlement")
swear <- c("hell", "damn", "fuck", "bitch", "bitch", "ass", "asshole", "bastard", "shit", "bloody", "hellfire", "motherfucker", "crap", "piss", "bollocks", "wanker", "bugger")
violence <- c("violence", "fight", "attack", "assault", "battle", "war", "weapon", "blood", "kill", "murder", "homicide", "gun", "knife", "bullet", "shot", "stab", "punch", "strangle", "choke", "brutal", "beating", "injure", "wound", "trauma", "hurt", "pain", "suffering", "death", "hit")

  alcohol_count <- 0
  intimacy_count <- 0
  family_count <- 0
  drugs_count <- 0
  guns_count <- 0
  music_count <- 0
  sad_count <- 0
  countylivin_count <- 0
  town_count <- 0
  swear_count <- 0
  violence_count <- 0
  
# Input: a data set with columns for lyrics, artist, and Title, and input a title for the graph
# Output and purpose: create a graph that shows the proportion of songs that contain a word from each theme
ThemeGraph <- function(TopGenre, graph_title) {
# Loop through each row of the lyrics column in TopGenre
for (lyric in TopGenre$lyrics) {
  # Check if any word from each vector is present in the lyrics
  if (any(grepl(paste(alcohol, collapse = "|"), lyric, ignore.case = TRUE))) {
    alcohol_count <- alcohol_count + 1
  }
  if (any(grepl(paste(intimacy, collapse = "|"), lyric, ignore.case = TRUE))) {
    intimacy_count <- intimacy_count + 1
  }
  if (any(grepl(paste(family, collapse = "|"), lyric, ignore.case = TRUE))) {
    family_count <- family_count + 1
  }
  if (any(grepl(paste(drugs, collapse = "|"), lyric, ignore.case = TRUE))) {
    drugs_count <- drugs_count + 1
  }
  if (any(grepl(paste(guns, collapse = "|"), lyric, ignore.case = TRUE))) {
    guns_count <- guns_count + 1
  }
  if (any(grepl(paste(music, collapse = "|"), lyric, ignore.case = TRUE))) {
    music_count <- music_count + 1
  }
  if (any(grepl(paste(sad, collapse = "|"), lyric, ignore.case = TRUE))) {
    sad_count <- sad_count + 1
  }
  if (any(grepl(paste(countylivin, collapse = "|"), lyric, ignore.case = TRUE))) {
    countylivin_count <- countylivin_count + 1
  }
  if (any(grepl(paste(town, collapse = "|"), lyric, ignore.case = TRUE))) {
    town_count <- town_count + 1
  }
  if (any(grepl(paste(swear, collapse = "|"), lyric, ignore.case = TRUE))) {
    swear_count <- swear_count + 1
  }
  if (any(grepl(paste(violence, collapse = "|"), lyric, ignore.case = TRUE))) {
    violence_count <- violence_count + 1
  }
}

# Create a data frame to store the counts
total_counts <- data.frame(
  vector = c("Alcohol", "Intimacy", "Family", "Drugs", "Guns", "Music", "Sad", "Country Living", "Town", "Swear", "Violence"),
  count = c(alcohol_count, intimacy_count, family_count, drugs_count, guns_count, music_count, sad_count, countylivin_count, town_count, swear_count, violence_count)
)

# Make counts into proportions so we can compare across genres
total_counts$proportion <- total_counts$count / sum(total_counts$count)

# Create a bar chart using ggplot with proportions
ggplot(total_counts, aes(x = vector, y = proportion)) +
  geom_bar(stat = "identity", fill="skyblue3") +
  labs(title = graph_title,
       x = "Themes",
       y = "Proportion of Songs with Words in Themes") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5))
}

ThemeGraph(TopHipHopSongsCSV, "Proportions of Themes Found in Hip Hop Songs")
ThemeGraph(TopCountry, "Proportions of Themes Found in Country Songs")
```

For our final analysis, we wanted to explore themes within song lyrics by tracking repetitiveness of certain words. Both Country music and Hip Hop have common stereotypes, and we wanted to see if these stereotypes are as apparent as they are thought to be. The themes that we looked for include words or short phrases relating to "Alcohol", "Intimacy", "Family", "Drugs", "Guns", "Music", "Sad", "Country Living", "Town", "Swear", and "Violence". We chose these themes and words that we might think belong in them, so this analysis may be lacking certain words or phrases that others might think to include. Because of this these plots may not fully depict all possible themes or trends within them.

When looking at the bar graph for Country, we can see that words relating to Alcohol, Country Living, Intimacy, and Violence seem to be the most repetitive. The themes of Drugs and Guns are very low, and Family, Music, Sad, Swear, and Town are all pretty moderate trends. 

When looking at the bar graph for Hip Hop, we can see that Intimacy, Swearing, and Violence are the most repetitive. Alcohol, Country Living, Drugs, Guns, and Town themes are all pretty moderately apparent, and the theme Sad appears the least according to our data collection. 

Words relating to Drugs and Guns appear more frequently in Hip Hop than Country music, which is something that many people might have suspected, although their differences are not as drastic as some might think. One interesting observation is that for both Country music and Hip Hop, Violence seems to be the most repeated theme. Another is that in Country, the theme country living would be the most common theme many people would use to describe country music, and words of that theme are very present in the lyrics we have collected. For Hip Hop, many stereotypes for the genre would be relating to swearing, violence, sex, drugs, and guns and these are themes that are notible in our collection, but an interesting observation is that themes relating to Family appear more than drugs or guns. 

When looking at the two plots we can see that for both Country and Hip Hop, there are certain themes that fit "stereo-typically" with the different genres that confirm these trends, although there are some surprising themes for both Country and Hip Hop found. Overall, I think that it is important not to oversimplify one genre based off of stereotypes that one might see.
  