title: "Final Project - Song Repetitiveness"
author: "Eva, Julia, Sophie, and Tessa"
date: "2024-05-07"
output:
  html_document:
    df_print: paged
=======
title: "Super Awesome Project Template"
output: word_document
date: "2023-03-31"


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rvest)
library(stringr)
library(tidytext)
library(dplyr)
library(tidyr)
library(ggplot2)
library(data.table)
```


For this project, our goal was to gather song data, and then analyze the song lyrics for repetitiveness in various ways. 
•	To start, we scraped Billboard Top 100 song data off of Wikipedia, and created a data frame with some basic information about each song.
•	We then used the data frame of songs to write a function to gather corresponding lyrics from the lyric hosting website www.songlyrics.com.
•	Once we had our cleaned up data frame of song information, we were then able to create functions to measure receptiveness and show them through multiple graphical visuals. 


To start the process of analyzing song lyrics, we first created a data frame with the Billboard Top Country songs starting from 1958 when the Billboard charts were first introduced. We included the top song titles and their corresponding artist, year, and genre. We then used this data frame to get lyrics for each song by scraping a song lyrics website. We also had to modify the title and artist names to best match the URL’s for the lyrics website, in order to maximize the number of songs we could get lyrics for. 



## Country Data
```{r, warning=FALSE, eval=FALSE}

#Sophies#####
#Use URLs to get song titles, artists, and dates
urlfunction <- function(year) {
  if (year == 1958 || (year >= 2012 && year <= 2023)) {
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Billboard_number-one_country_songs_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, "td:nth-child(3) .fn a , th+ td > a")
  }else if (year >= 1959 && year <= 1961){
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_C%26W_Sides_number_ones_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, ".jquery-tablesorter span a , .jquery-tablesorter th a")
  }else if (year >= 1962 && year <= 1989) {
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_Country_Singles_number_ones_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, ".fn a , td > a")
  }else if (year >= 1990 && year <= 2004) {
      country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_Country_Singles_%26_Tracks_number_ones_of_",  year)
      html <- read_html(country_url)
      cast <- html_nodes(html, ".jquery-tablesorter th+ td a , .jquery-tablesorter th a")
  }else { 
    country_url <- paste0("https://en.wikipedia.org/wiki/List_of_Hot_Country_Songs_number_ones_of_",  year)
    html <- read_html(country_url)
    cast <- html_nodes(html, ".jquery-tablesorter th+ td a , .jquery-tablesorter th a")
  }  

  html_text(cast, trim = TRUE) 
  tables <- html_table(html, fill = TRUE, header = TRUE)
  desired_table <- tables[[1]]
  desired_table <- desired_table[, c(2, 3)]
    #include only the second and third columns which are title and artist
  if ("Title" %in% desired_table[1, ]) {
    desired_table <- desired_table[-1, ]
    #get rid of top row if they have an extra header row
          }
  colnames(desired_table) <- c("Title", "Artist")
    #name columns
  desired_table$Year <- year
     #add columns for year
  desired_table$genre <- "Country" 
     #add column for genre
  desired_table <- unique(desired_table)
    #get rid of repeat columns
  return(desired_table)
      
}
TopSongs <- data.frame()
for(year in 1958:2023){
    current_year <- urlfunction(year)
    TopSongs <- rbind(TopSongs, current_year)
}



#Julia#####

#remove slash and everything behind it
TopSongs$Title<-gsub("/.*", "", TopSongs$Title)

#remove quotation marks
TopSongs$Title<-gsub('"', '', TopSongs$Title)

#new data frame with dashes instead of spaces for url purposes
TopSongs2 <- sapply(TopSongs, function(x) gsub(" ", "-", x))

# Modify artist and title names
TopSongs2 <- as.data.frame(TopSongs2)
TopSongs2$Title <- sub("-$", "", TopSongs2$Title)
TopSongs2$Title <- gsub("[,.?%()]", "", TopSongs2$Title)
TopSongs2$Artist <- gsub("[.']", "", TopSongs2$Artist)
TopSongs2$Artist <- sub("-and", "", TopSongs2$Artist)

```

```{r, warning=FALSE}
# Purpose: This function scrapes lyrics from songlyrics.com for the billboard top 100 country songs 
# Input: Our songs data frame
# Output: A new column in the songs data frame with lyrics for every song
scrape_lyrics <- function(df) {
  lyrics <- character(nrow(df))  
  for (i in 1:nrow(df)) {
    url <- paste0("https://www.songlyrics.com/", df$Artist[i], "/", df$Title[i], "-lyrics/")
    # Tests for errors when getting URLs and makes sure code keeps running after an error occurs
    tryCatch({
      html <- read_html(url)
      raw_lyrics <- html_nodes(html, "#songLyricsDiv") %>% html_text() %>% as.character()
      lyrics[i] <- paste(raw_lyrics, collapse = " ")
    }, error = function(e) {
    })
  }
  df$lyrics <- lyrics  
  return(df)
}
# Apply function to our data frame
TopSongs3 <- scrape_lyrics(TopSongs2)
```

```{r, warning=FALSE}
###EVA#####
# Modifies song lyrics to match
TopSongs3$lyrics <- gsub("\n", " ", TopSongs3$lyrics)
TopSongs3$lyrics <- gsub("[,.()]", "", TopSongs3$lyrics)
TopSongs3$lyrics <- tolower(TopSongs3$lyrics)
# Remove rows with missing lyrics
TopSongs3 <- subset(TopSongs3, !(is.na(lyrics) | lyrics == ""))
TopSongs3 <- subset(TopSongs3, !grepl("we do not have the lyrics for", lyrics))


##JULIA###
#getting rid of duplicate songs
TopSongs3 <- TopSongs3[!duplicated(TopSongs3$Title), ]

#get rid of the dashes and make them spaces
TopSongs3$Title <- gsub("-", " ", TopSongs3$Title)
TopSongs3$Artist <- gsub("-", " ", TopSongs3$Artist)

#change title and artist to all lower case
TopSongs3$Title<-tolower(TopSongs3$Title)
TopSongs3$Artist<-tolower(TopSongs3$Artist)


#save it as a csv file to working directory
write.csv(TopSongs3, "TopCountry.csv", row.names = FALSE)

#call it to test that it works and reads it correctly
TopCountry<-read.csv("TopCountry.csv")


```

RAP CODE 
```{r, warning=FALSE}
#input: a year
#output and purpose: create a table of the top rap songs from that year
urlfunctionHipHop <- function(year) {
  if (year >= 2007 && year <= 2023) {
      HipHop_url <- paste0("https://en.wikipedia.org/wiki/List_of_number-one_R%26B/hip-hop_songs_of_", year, "_(U.S.)")
      #specific url for years 2007-2023
      html <- read_html(HipHop_url)
      cast <- html_nodes(html, "th , .plainrowheaders td")
      html_text(cast, trim = TRUE) 
      tables <- html_table(html, fill = TRUE, header = TRUE)
      #accessing the desired table
      if (year == 2012) {
        #the table containing the artist and song title from the website differed for the year 2012
        desired_table <- tables[[1]]
      }else{
        desired_table <- tables[[2]]
      }
      desired_table <- desired_table[, -1]
        #taking out an unnecessary first column
  }else {
      #specific url for every year before 2007
      HipHop_url <- paste0("https://en.wikipedia.org/wiki/", year, "_in_hip_hop_music")
      html <- read_html(HipHop_url)
      cast <- html_nodes(html, ".headerSort , .jquery-tablesorter td, .headerSort") 
      html_text(cast, trim = TRUE) 
      tables <- html_table(html, fill = TRUE, header = TRUE)
      #accessing the desired table
      if (year == 2000 || year >= 2002) {
        #the table containing the artist and song title from the website differed for years 2000 and from 2002-2006
        desired_table <- tables[[5]]
      }else{
        desired_table <- tables[[6]]
      }
  }
  colnames(desired_table) <- c("Title", "Artist")
    #name columns
  desired_table$Year <- year
     #add columns for year
  desired_table$genre <- "Rap" 
     #add column for genre
  desired_table <- unique(desired_table)
     #take out repeated rows
  return(desired_table)
}

TopHipHopSongs <- rbindlist(lapply(1986:2023, urlfunctionHipHop), fill = TRUE)
  #run the function to find tables and put them together from years 1986 to 2023
  #we picked 1987 because this was the first year that there was top hip hop songs in Wikipedia
TopHipHopSongs <- TopHipHopSongs[,c(1,2,5,6), drop = FALSE]
  #only including , artist, year,  and genre
TopHipHopSongs <- unique(TopHipHopSongs)
  #deleting repeat columns
DFTopHipHopSongs <- as.data.frame(TopHipHopSongs)
DFTopHipHopSongs$Title<-gsub('"', '', DFTopHipHopSongs$Title)
DFTopHipHopSongs <- sapply(DFTopHipHopSongs, function(x) gsub(" ", "-", x))
DFTophipHopSongs <- as.data.frame(DFTopHipHopSongs)
DFTopHipHopSongs$Title <- sub("-$", "", DFTopHipHopSongs$Title)
DFTopHipHopSongs$Title <- gsub("[,.?%()]", "", DFTopHipHopSongs$Title)
DFTopHipHopSongs$Artist <- gsub("[.']", "", DFTopHipHopSongs$Artist)
DFTopHipHopSongs$Artist <- sub("-and", "", DFTopHipHopSongs$Artist)

LyricsHipHopRapSongs3 <- scrape_lyrics(DFTopHipHopSongs)

# Modifies song lyrics to match
LyricsTopRapSongs3$lyrics <- gsub("\n", " ", LyricsTopRapSongs3$lyrics)
LyricsTopRapSongs3$lyrics <- gsub("[,.()]", "", LyricsTopRapSongs3$lyrics)
LyricsTopRapSongs3$lyrics <- tolower(LyricsTopRapSongs3$lyrics)
# Remove rows with missing lyrics
LyricsTopRapSongs3 <- subset(LyricsTopRapSongs3, !(is.na(lyrics) | lyrics == ""))
LyricsTopRapSongs3 <- subset(LyricsTopRapSongs3, !grepl("we do not have the lyrics for", lyrics))
# Remove dashes between title and artist
LyricsTopRapSongs3$Title<-gsub("-", " ", LyricsTopRapSongs3$Title)
LyricsTopRapSongs3$Artist<-gsub("-", " ", LyricsTopRapSongs3$Artist)

write.csv(LyricsTopRapSongs3, "TopRapSongs.csv", row.names = FALSE)
TopRapSongsCSV <-read.csv("TopRapSongs.csv")
```


## Measure of Repetitivness: Unqiue Words Ratio - Tessa
```{r, warning=FALSE}
# UNIQUE RATIO FUNCTION WITH GRAPH
# Purpose: To generate a ratio of unique words to total words within song lyrics for each year included in the data frame and create a ggplot of the resulting data.
# The function inputs: The input of this function is a data frame, which must have columns with "year" and "lyrics". It also take in graph_title which allows you to specifically name your graph.
# The function output: The function return a data frame with columns of year, total words, unique words, and unique ratio. The function will print the graph out showing a trend of unqiue word ratio over time.
generate_unique_ratios_graph <- function(song_df, graph_title) {

generate_unique_ratios <- function(song_df) {
  # make lyrics into single words using tidytext package
  token_lyrics <- song_df %>%
    unnest_tokens(words, lyrics) %>%
    mutate(Year = Year)  # include year data

  # Group by year and calculate unique words ratio
  unique_words_by_year <- token_lyrics %>%
    group_by(Year) %>%  # group lyrics by year
    summarise(total_words = n(), # find total words
              unique_words = n_distinct(words), # find unique words using dplyr (n_distincy)
              ratio = unique_words / total_words) # find ratio of unique words to total words

  return(unique_words_by_year)
}
# low ratio means songs are more repetitive
unique_words_ratios <- generate_unique_ratios(song_df)

# find the overall unique words ratio to add to graph:
overall_unique_words_ratio <-mean(unique_words_ratios$ratio)

# find middle of years so the label is in the middle of the graph
x_midpoint <- median(unique_words_ratios$Year)

# graph unique words ratio over the years
unique_ratio_graph_by_year <-ggplot(unique_words_ratios, aes(x = Year, y = ratio)) +
  geom_line() +
  geom_hline(yintercept = overall_unique_words_ratio, color = "skyblue3") + #add an hline to show when the data is above and below average
  annotate("text", x = x_midpoint, y = overall_unique_words_ratio + 0.01, label = "Average Unique Words Ratio", color = "skyblue3" ) +  # add label to represent what hline means
  labs(title = graph_title,
       x = "Year",
       y = "Unique Words Ratio") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5)) # center title

return(unique_ratio_graph_by_year)
}

Country_Unique_Ratio_Graph <-generate_unique_ratios_graph(TopCountry, "Unique Words Ratio of Top Country Songs Over Time")
Country_Unique_Ratio_Graph
Rap_Unique_Ratio_Graph <-generate_unique_ratios_graph(TopRapSongsCSV, "Unique Words Ratio of Top Rap Songs Over Time")
Rap_Unique_Ratio_Graph

```

## Measure of Receptiveness: Title Repetition - Tessa and Julia
```{r, warning=FALSE}
# TITLE REPETITION FUNCTION WITH GRAPH INCLUDED
# Purpose: To find the number of times a song repeats its title within its own lyrics. Then add the frequency of repeats to the inputted data frame. Lastly it will provide a graph of average title repeats over time with a linear regression model to see if there is a linear relationship.
# The function inputs: The input of this function is a data frame, which must have columns with "Title", "Year", and "lyrics".
# The function output: The function returns the inputted data frame, along with a column called repeats. It will print out a graph showing average title repeats over time with a fitted linear regression model. It will also output some summary statistics of the fitted model.
generate_title_repetition_graph <- function(song_df, graph_title) {
  # Initialize empty column called repeats to hold frquency
  song_df$repeats <- numeric(nrow(song_df))
  
  # for each row in inputted data frame:
  for (i in 1:nrow(song_df)) {
    title <- tolower(song_df$Title[i])  # extract title
    lyrics <- tolower(song_df$lyrics[i]) # extract lyrics
    
    # sum number of times the title is in the lyrics
    title_count <- sum(gregexpr(title, lyrics)[[1]] > 0)
    
    # add repeats count to the existing data frame
    song_df$repeats[i] <- title_count
  }
  
  #create table with average title repeats within each song per year
  ave_title_repeats_by_year <- song_df %>%
    group_by(Year) %>%
    summarize(AveTitleRepeats = mean(repeats))
  
  # plot data by year
  ave_title_repeats <-
    ggplot(ave_title_repeats_by_year, aes(x = Year, y = AveTitleRepeats)) +
    geom_point(size = 1.2) +
    geom_smooth(method = "lm", se = FALSE, color = "skyblue3") +
    labs(title = graph_title,
         x = "Year",
         y = "Mean Title Repeats Per Year") +
    theme_minimal() +
    scale_y_continuous(limits = c(0, NA), breaks = seq(0, max(
      ave_title_repeats_by_year$AveTitleRepeats
    ), by = 5)) + theme(plot.title = element_text(hjust = 0.5))
  
  print(ave_title_repeats)
  
  res2 <- lm(AveTitleRepeats ~ Year, ave_title_repeats_by_year)
  print(summary(res2))
  
}

Country_Title_Repetition <-generate_title_repetition_graph(TopCountry, "Average Title Repeats of Top Country Over Time")
Country_Title_Repetition
Rap_Title_Repetition <-generate_title_repetition_graph(TopRapSongsCSV, "Average Title Repeats of Top Rap Over Time")
Rap_Title_Repetition

```

The figures above represent the average amount of times each title was repeated within its song lyrics per charting year. For country music we have data that can be visualized from 1958 to 2019. When looking at our plot for country, we can see an upward trend within the points, so we can say that over time song titles are increasingly being repeated in lyrics. We decided to fit a linear model to the data, and after observing the summary statistics we can see that the model fits moderately well with an R squared statistic of 0.3169. Time is explaining about 31.7% of the variance in title repetition. 

For Hip Hop, we have data that can be visualized from 1987 to 2023. Interestingly enough, we can see a downward trend in the repetition over time. It seems that over time, titles of songs are repeated less on average in lyrics. Unlike country music, a linear model does not fit very well to this model. Time in years can explain about 8.312% of the variance in the data points according to an R-squared statistic of 0.08312. In the figure for Hip Hop, the year 1990 stands out because of its high average repetition. In 1990 the top Hip Hop songs included "Ice Ice Baby" by Vanilla Ice, "Have you Seen her","Pray", and "U Can't Touch This" by MC Hammer, and "Just a Friend" by Biz Markie. The lyrics of these songs are extremely repetitive, which explains why this year has a high average. 

Why are song titles being repeated more in Country and less in Hip Hop over time? One inference could be that country artists want to include the title of their songs in their music to enhance the listeners recall and remembrance of the song. Since the 1960s, the way musicians earn profit has changed, and artists may be focusing more on streams instead of selling records and cds. Another could be that over time the genre has shifted into more of a pop culture which is generally more repetitive. For Hip Hop, one inference could be that Hip Hop has grown in popularity over time and because of this, the genre has expanded in many ways. Hip Hop has developed into many sub genres and has become more diverse. 

When comparing the two genres, we do have to keep in mind the fact that our collected country data has a sample size of 1460 that stretches over 61 years, while the Hip Hop genre has a sample size of 305, and only stretches 36 years of observation. Because our data for the country genre holds a larger sample size, we can see more of an accurate representation of trends within the genre. The sample size for Hip Hop is a lot smaller, and so our figures may not fully represent the genre.


## Sophie
```{r, warning=FALSE}
alcohol <- c("whiskey", "moonshine", "beer", "wine", "tequila", "vodka", "jack daniels", "budlight", "coorslight", "busch", "alcohol", "rum", "gin", "brandy", "cognac", "schnapps", "absinthe", "champagne", "sake")
intimacy <- c("sexy", "hot", "sex", "attractive", "baby", "babe", "lover", "sweetheart", "passion", "desire", "romance", "affection", "intimacy", "seductive", "lust")
family <- c("mom", "mama", "granny", "marriage", "children", "marry", "wife", "husband", "dogs", "father", "daddy", "grandpa", "grandmother", "aunt", "uncle", "cousin", "siblings", "in-laws", "offspring")
drugs <- c("coke", "cocaine", "tabacco", "weed", "heroin", "methamphetamine", "LSD", "ecstasy", "prescription drugs", "opioids", "hallucinogens", "MDMA", "smoke", "smoking")
guns <- c("gun", "guns", "revolver", "shotgun", "rifle", "pistol", "firearm", "ammunition", "sniper", "handgun", "arsenal")
music <- c("melody", "rhythm", "harmony", "lyrics", "genre", "beat", "album", "artist", "band", "guitar")
sad <- c("heartbreak", "sorrow", "grief", "despair", "melancholy", "misery", "anguish", "heartache", "depression", "tears")
countylivin <- c("cowboy", "horse", "truck", "pickup", "road", "tea", "tractor", "barn", "ranch", "cattle", "hay", "pasture", "cowboy boots", "western", "yeehaw", "rodeo")
town <- c("small town", "hometown", "back home", "home", "village", "community", "neighborhood", "suburb", "township", "locality", "settlement")
swear <- c("hell", "damn", "fuck", "bitch", "bitch", "ass", "asshole", "bastard", "shit", "bloody", "hellfire", "motherfucker", "crap", "piss", "bollocks", "wanker", "bugger")
violence <- c("violence", "fight", "attack", "assault", "battle", "war", "weapon", "blood", "kill", "murder", "homicide", "gun", "knife", "bullet", "shot", "stab", "punch", "strangle", "choke", "brutal", "beating", "injure", "wound", "trauma", "hurt", "pain", "suffering", "death", "hit")

  alcohol_count <- 0
  intimacy_count <- 0
  family_count <- 0
  drugs_count <- 0
  guns_count <- 0
  music_count <- 0
  sad_count <- 0
  countylivin_count <- 0
  town_count <- 0
  swear_count <- 0
  violence_count <- 0
  
# Purpose:
# Input:
# Output:
ThemeGraph <- function(TopGenre, graph_title) {
# Loop through each row of the lyrics column in Topsongs2
for (lyric in TopGenre$lyrics) {
  # Check if any word from each vector is present in the lyrics
  if (any(grepl(paste(alcohol, collapse = "|"), lyric, ignore.case = TRUE))) {
    alcohol_count <- alcohol_count + 1
  }
  if (any(grepl(paste(intimacy, collapse = "|"), lyric, ignore.case = TRUE))) {
    intimacy_count <- intimacy_count + 1
  }
  if (any(grepl(paste(family, collapse = "|"), lyric, ignore.case = TRUE))) {
    family_count <- family_count + 1
  }
  if (any(grepl(paste(drugs, collapse = "|"), lyric, ignore.case = TRUE))) {
    drugs_count <- drugs_count + 1
  }
  if (any(grepl(paste(guns, collapse = "|"), lyric, ignore.case = TRUE))) {
    guns_count <- guns_count + 1
  }
  if (any(grepl(paste(music, collapse = "|"), lyric, ignore.case = TRUE))) {
    music_count <- music_count + 1
  }
  if (any(grepl(paste(sad, collapse = "|"), lyric, ignore.case = TRUE))) {
    sad_count <- sad_count + 1
  }
  if (any(grepl(paste(countylivin, collapse = "|"), lyric, ignore.case = TRUE))) {
    countylivin_count <- countylivin_count + 1
  }
  if (any(grepl(paste(town, collapse = "|"), lyric, ignore.case = TRUE))) {
    town_count <- town_count + 1
  }
  if (any(grepl(paste(swear, collapse = "|"), lyric, ignore.case = TRUE))) {
    swear_count <- swear_count + 1
  }
  if (any(grepl(paste(violence, collapse = "|"), lyric, ignore.case = TRUE))) {
    violence_count <- violence_count + 1
  }
}

# Create a data frame to store the counts
total_counts <- data.frame(
  vector = c("Alcohol", "Intimacy", "Family", "Drugs", "Guns", "Music", "Sad", "Country Living", "Town", "Swear", "Violence"),
  count = c(alcohol_count, intimacy_count, family_count, drugs_count, guns_count, music_count, sad_count, countylivin_count, town_count, swear_count, violence_count)
)

# Make counts into proportions so we can compare across genres
total_counts$proportion <- total_counts$count / sum(total_counts$count)

# Create a bar chart using ggplot with proportions
ggplot(total_counts, aes(x = vector, y = proportion)) +
  geom_bar(stat = "identity") +
  labs(title = graph_title,
       x = "Themes",
       y = "Proportion of Songs with Words in Themes") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        plot.title = element_text(hjust = 0.5))
}

ThemeGraph(TopRapSongsCSV, "Proportions of Themes Found in Rap Songs")
ThemeGraph(TopCountry, "Proportions of Themes Found in Country Songs")
```

